### 2023-12-28 sections/1-introduction.tex
added applications for rho nn

{\color{red} TODO: Talk about common uses of $\rho$-NN search, as we do with $k$-NN search above.}

>>>>

$\rho$-NN search is also often used in a variety of applications, including finding evolutionarily-related organisms~\cite{budowski2010fragbag}, serving relevant advertisements to users~\cite{zhang2020privacy}, and suggesting corrections to misspelled words~\cite{ukkonen1985algorithms}.
{\color{red} TODO: Add another sentence here.}
